Evaluation

### 2019-02-27 evaluation.Rmd
Update evaluation.Rmd

```{r recent_eval, echo=FALSE, fig.width=7, fig.height=7}
plot_err_lead_spp_mods()
```

>>>>

This figure shows the raw error as a function of lead time (how far in advance the prediction was made) for three forecast dates (colors of lines) across each combination of model (column) and species (row) for a selection of historically common species and the total rodents, for the control (unmanipulated) plots only.

```{r recent_eval, echo=FALSE, fig.width=10, fig.height=10}
plot_err_lead_spp_mods()
```
